Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-03-15 supplement.tex
sync
supplement layout fixed
Fix typo; remove highlighting for revision 1

%% highlight changes for revision in red
\newcommand{\revised}[1]{{\color{red} #1}}
\newenvironment{revision}{\color{red}}{\color{black}}

@@

\begin{figure}[!h]
\textbf{A}~\includegraphicstop[width=0.48\textwidth]{Figs/Plots/stem_weight1-500_mean}%
\textbf{B}~\includegraphicstop[width=0.48\textwidth]{Figs/Plots/doublestem_weight1-500_mean}%
\caption{Comparison of uniform sampling and Boltzmann sampling with
weight $\pi=500$. We show results for two different small structures: (A) single stem structure (B) double stem structure. For each respective structure $R$, we plot the energies $E(S,R)$ of
10000 sampled sequences against the probabilities $Pr(R|S)$ (in log scale). For illustrating the trend, we show moving averages over windows of $\pm 1$ kcal. Note that while only the energy $E(S,R)$ is directly controlled by Boltzmann sampling, this strongly impacts the common negative design objective $Pr(R|S)$.}
\label{appfig:negforpos}
\end{figure}

@@

\revised{
  Finally, for further illustration, we show concrete tree decompositions for a selected instance in the benchmark set RF3 in Figure~\ref{appfig:td-example}. This figure is provided solely for illustrational purposes:
  First, it depicts the tree decomposition for a typical, realistic sampling task. Second, it exemplarily illustrates the typical impact of the energy model on the tree decomposition.
  Compared to the tree decomposition based on the stacking model, the tree decomposition for the base pair model is much simpler. This shows in many connected components, which correspond to independently solvable sub-problems, and fewer positions per bag (i.e. smaller tree width), which allows far more efficient evaluation per tree node. 
  Note that the complexity of the tree decomposition ultimately shows the complexity of the dependencies that need to be considered for simultaneous energy evaluation for all target structures. This complexity is substantially increased in the stacking model over the simpler base pair model.
}

\begin{revision}

@@

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.43\textwidth]{Figs/RunTimes/construction_time_sets}\quad%
  \includegraphics[width=0.43\textwidth]{Figs/RunTimes/sample_time_sets}
  \caption{Boxplots showing the run-time distribution of sequence sampling with \ourprog{} for the various benchmark sets. The times are split into construction time (left) and sampling time (right). Construction includes all the precomputation, while the latter is the time needed to generate 10000 sequences. }
  \label{appfig:run-times-redprint}
\end{figure}
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.43\textwidth]{Figs/RunTimes/construction_time_sets_rbp}\quad%
  \includegraphics[width=0.43\textwidth]{Figs/RunTimes/sample_time_sets_rbp}
  \caption{Boxplots showing the run-time distribution of sequence sampling with \RNAblueprint{} for the various benchmark sets. The times are split into construction time (left) and sampling time (right). Construction includes all the precomputation, while the latter is the time needed to generate 10000 sequences.}
  \label{appfig:run-times-rbp}
\end{figure}

@@

\end{revision}

@@

\begin{figure}[h!]
      \begin{center}
        %{\sf \bfseries A}\includegraphicstop[width=0.32\textwidth]{Figs/offset2}\hspace{.5cm}
        %{\sf \bfseries B}
        \includegraphicstop[width=0.8\textwidth]{Figs/energy_distribution}
      \end{center}
      \caption{%
        Targeting specific energies using multi-dimensional Boltzmann
        sampling. We show the Turner energy distributions for
        three target structures R1, R2 and R3. \revised{By
        targeting the respective free energies ($-40$, $-40$ and $-20$\,kcal/mol and $-20$,$-20$ and $-20$\,kcal/mol) for the target structures (annotated in red and
        blue, respectively), we demonstrate the
        effectivity of our adaptive multi-dimensional Boltzmann sampling
        procedure. Moreover, }for comparison, the distributions for uniform
        (U) and Boltzmann (B) samples---respectively associated with
        homogeneous weights $1$ and $e^\beta$.
%    ($\delta=0.05, \delta'=0.1, \gamma=1.1, \psi=20, n=1000$)
  }
  \label{appfig:energydist}
\end{figure}

@@

\begin{revision}
\section{Effectivity of the seed sequence generation}
\label{appsec:effectivity-seed-generation}

>>>>

%% revised for first revision
\newcommand{\revisedOne}[1]{#1}
\newenvironment{revisionOne}{}{}
%%revised for second minor/discretionary revision
\newcommand{\revised}[1]{{\color{red!60!black} #1}}
\newenvironment{revision}{\color{red}}{\color{black}}

@@

\begin{figure}[!h]
\textbf{A}~\includegraphicstop[width=0.48\textwidth]{Figs/Plots/stem_weight1-500_mean}%
\textbf{B}~\includegraphicstop[width=0.48\textwidth]{Figs/Plots/doublestem_weight1-500_mean}%
\caption{Comparison of uniform sampling and Boltzmann sampling with
weight $\pi=500$. We show results for two different small structures: (A) single stem structure (B) double stem structure. For each respective structure $R$, we plot the energies $E(S,R)$ of
10\,000 sampled sequences against the probabilities $Pr(R|S)$ (in log scale). For illustrating the trend, we show moving averages over windows of $\pm 1$ kcal. Note that while only the energy $E(S,R)$ is directly controlled by Boltzmann sampling, this strongly impacts the common negative design objective $Pr(R|S)$.}
\label{appfig:negforpos}
\end{figure}

@@

\revisedOne{
  Finally, for further illustration, we show concrete tree decompositions for a selected instance in the benchmark set RF3 in Figure~\ref{appfig:td-example}. This figure is provided solely for illustrational purposes:
  First, it depicts the tree decomposition for a typical, realistic sampling task. Second, it exemplarily illustrates the typical impact of the energy model on the tree decomposition.
  Compared to the tree decomposition based on the stacking model, the tree decomposition for the base pair model is much simpler. This shows in many connected components, which correspond to independently solvable sub-problems, and fewer positions per bag (i.e. smaller treewidth), which allows far more efficient evaluation per tree node. 
  Note that the complexity of the tree decomposition ultimately shows the complexity of the dependencies that need to be considered for simultaneous energy evaluation for all target structures. This complexity is substantially increased in the stacking model over the simpler base pair model.
}

\begin{revisionOne}

@@

\begin{figure}[hb!]
  \centering
  \includegraphics[width=0.43\textwidth]{Figs/RunTimes/construction_time_sets}\quad%
  \includegraphics[width=0.43\textwidth]{Figs/RunTimes/sample_time_sets}
  \caption{Boxplots showing the run-time distribution of sequence sampling with \ourprog{} for the various benchmark sets. The times are split into construction time (left) and sampling time (right). Construction includes all the precomputation, while the latter is the time needed to generate 10000 sequences. }
  \label{appfig:run-times-redprint}
\end{figure}
\begin{figure}[hb!]
  \centering
  \includegraphics[width=0.43\textwidth]{Figs/RunTimes/construction_time_sets_rbp}\quad%
  \includegraphics[width=0.43\textwidth]{Figs/RunTimes/sample_time_sets_rbp}
  \caption{Boxplots showing the run-time distribution of sequence sampling with \RNAblueprint{} for the various benchmark sets. The times are split into construction time (left) and sampling time (right). Construction includes all the precomputation, while the latter is the time needed to generate 10000 sequences.}
  \label{appfig:run-times-rbp}
\end{figure}

@@

@@

\end{revisionOne}

@@

\begin{figure}[h!]
      \begin{center}
        %{\sf \bfseries A}\includegraphicstop[width=0.32\textwidth]{Figs/offset2}\hspace{.5cm}
        %{\sf \bfseries B}
        \includegraphicstop[width=0.8\textwidth]{Figs/energy_distribution}
      \end{center}
      \caption{%
        Targeting specific energies using multi-dimensional Boltzmann
        sampling. We show the Turner energy distributions for
        three target structures R1, R2 and R3. \revisedOne{By
        targeting the respective free energies ($-40$, $-40$ and $-20$\,kcal/mol and $-20$,$-20$ and $-20$\,kcal/mol) for the target structures (annotated in red and
        blue, respectively), we demonstrate the
        effectivity of our adaptive multi-dimensional Boltzmann sampling
        procedure. Moreover, }for comparison, the distributions for uniform
        (U) and Boltzmann (B) samples---respectively associated with
        homogeneous weights $1$ and $e^\beta$.
%    ($\delta=0.05, \delta'=0.1, \gamma=1.1, \psi=20, n=1000$)
  }
  \label{appfig:energydist}
\end{figure}

@@

\begin{revisionOne}
\section{Effectivity of the seed sequence generation}
\label{appsec:effectivity-seed-generation}
